---
title: This is the Greatest and Best Paper in the World (Tribute)
documentclass: svjour3
output: 
###########
  # html_document:
  #  template: default
###########
  #bookdown::pdf_document2:
    #template: main.tex
    # keep_tex: true
    # fig_caption: true
###########
  # bookdown::pdf_book:
  #   includes:
  #     in_header: latex/preamble.tex
  #     before_body: latex/before_body.tex
  #     after_body: latex/after_body.tex
  #   keep_tex: yes
  #   citation_package: natbib
###########
  rmarkdown::pdf_document:
    template: main.tex
    keep_tex: true
    fig_caption: true
###########
  # rmarkdown::word_document:
    # template: main.tex
    # keep_tex: true
    # fig_caption: true
###########    
abstract: This is the greatest and best abstract in the world. Tribute.
bibliography: my-bibliography.bib
biblio-style: "spbasic"
link-citations: true
---

<!-- Examples & Help

Create Awesome LaTeX Table with knitr::kable and kableExtra
https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf



-->

```{r setup, include=FALSE, message=FALSE}
library(pacman)
library(tidyverse)
library(hash)
p_load(bookdown)
load("C:/GIT_clones/BAFU_Strompreise/cache/munged/munged.spotPrices.Phelix.Rdata")
x <- hash()
x["Total Consumption"] <- spotPrices.Phelix$Phelix_EUR_MWh %>% mean()
```

# Introduction

dbhdskjfds
"Tribute" is the first single of Tenacious D's self-titled debut album[@Cowan1988; @Whittaker2016-time-info]. It was released `r round(x[["Total Consumption"]],1)` times July 16, 2002. The song is a tribute to what Gass and Black refer to as "The Greatest Song in the World" (often confused as the song's title), which Tenacious D themselves came up with, but have since forgotten. It was released as a downloadable track for Rock Band in addition to appearing as a playable track for Guitar Hero Live.[@Hume1748]

# History
Tribute was the first song Black and Gass played live as Tenacious D. The song, like many other songs that were recorded on Tenacious D, was originally performed on their short-lived HBO TV series. During earlier performances of this song Kyle Gass played the opening to "Stairway to Heaven". The two songs are both in A minor and have very similar chord progressions, and critics have said the songs sound alike.[@Cowan1988; @Gluck2005; @Wardak2002] **The maturation of the song over time is shown in Figure \@ref(fig:tribute-plot).**

```{r tribute-plot, echo=FALSE, out.width='0.98\\columnwidth', fig.cap=keys(x["Total Consumption"])}
plot(pressure)
```

```{r two-col-tribute-plot, echo=FALSE, out.width='0.98\\textwidth', fig.cap="This is a two-column plot of how great Tribute gets over time", fig.env='figure*'}
plot(pressure)
```


```{r two-col-tribute-plot2, echo=FALSE, out.width='0.98\\textwidth', fig.cap="Neu", fig.env='figure*'}
plot(pressure)
```

## Synopsis
The song chronicles the band members' encounter with a demon who demands the duo play "the best song in the world" or have their souls eaten. Having nothing to lose from trying, they play "the first thing that came to our heads", and it "just so happened to be the best song in the world."[@Wardak2002]

```{r table-iris, echo=FALSE}
iris %>%
  select(-Species) %>%
  head(10) %>%
  knitr::kable(format = "latex", booktabs = TRUE, caption = "The favorite iris' of Tenacious D.")
```


Given the "Stairway to Heaven" interlude in the original TV series version, along with the similarity of the chord progression in both songs, Tribute at first implies that the best song in the world is indeed that song. However, the lyrics make clear that Tribute sounds nothing like the song they came up with to please the demon; as Black describes: "And the peculiar thing is this my friends: The song we sang on that fateful night, it didn't actually sound anything like this song."

